Challenges in Developing Great MCQMC Software

### 2022-07-13 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

%Talk given at MCQMC 2022 July
\documentclass[11pt,compress,xcolor={usenames,dvipsnames},aspectratio=169]{beamer}
%\documentclass[xcolor={usenames,dvipsnames},aspectratio=169]{beamer} %slides and 
%notes
\usepackage{amsmath,
	amssymb,
	datetime,
	mathtools,
	bbm,
	%mathabx,
	array,
	booktabs,
	xspace,
	multirow,
	calc,
	colortbl,
	siunitx,
 	graphicx}
\usepackage[usenames]{xcolor}
\usepackage[giveninits=false,backend=biber,style=nature,style=authoryear,maxcitenames =10, mincitenames=9]{biblatex}
\addbibresource{FJHown23.bib}
\addbibresource{FJH23.bib}
\usepackage{newpxtext}
\usepackage[euler-digits,euler-hat-accent]{eulervm}
\usepackage{media9}
\usepackage[autolinebreaks]{mcode}
\usepackage[tikz]{mdframed}

@@

\renewcommand{\OffTitleLength}{-7ex}
\setlength{\FJHThankYouMessageOffset}{-8ex}
\title{Challenges in Developing Great MCQMC Software}
\author[]{Fred J. Hickernell}
\institute{Department of Applied Mathematics \&
	Center for Interdisciplinary Scientific Computation \\  Illinois Institute of Technology \quad
	\href{mailto:hickernell@iit.edu}{\url{hickernell@iit.edu}} \quad
	\href{http://mypages.iit.edu/~hickernell}{\url{mypages.iit.edu/~hickernell}}}

\thanksnote{with Mark Klinchin and the rest of the GAIL an QMCPy teams \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Thanks to the organizers as we meet again in person in still challenging times\\
	Slides at  \href{https://speakerdeck.com/fjhickernell/quasi-monte-carlo-software}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022}
\date[]{July 18, 2022}

@@

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item \textcite{LEc2017a} provides a history of \alert{random number generation}
		\item Notorious \alert{\texttt{randu}} from the 1960s \parencite{RANDU}, which fails the spectral test
		\item \alert{\texttt{VEGAS}} \parencite{Lep78a, Lep21a} importance sampling Monte Carlo algorithm favored by physicists
		\item \alert{ACM} low discrepancy point generators \parencite{BraFox88,BraFoxNie92,HonHic00a}
		\item FinDer \parencite{PasTra95,FinDer} and BRODA \parencite{BRODA20a} targeting quantitative finance
		\item Korobov cubature and scrambled Sobol' generators in \alert{NAG} \parencite{NAG27} for decades		
		\item Scrambled Sobol' and Halton generators in \textcite{MAT9.13} since 2008
	\end{itemize}
\end{frame}

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item Scrambled Sobol' and Halton generators in \textcite{MAT9.13} since 2008
		\item Scrambled Sobol' in SciPy \parencite{virtanen2020scipy} and PyTorch \parencite{paszke2019pytorch}

@@

\printbibliography
\end{document}

>>>>

%Talk given at MCQMC 2022 July
\documentclass[11pt,compress,xcolor={usenames,dvipsnames},aspectratio=169]{beamer}
%\documentclass[xcolor={usenames,dvipsnames},aspectratio=169]{beamer} %slides and 
%notes
\usepackage{amsmath,
	amssymb,
	datetime,
	mathtools,
	bbm,
	%mathabx,
	array,
	booktabs,
	xspace,
	multirow,
	calc,
	colortbl,
	siunitx,
 	graphicx}
\usepackage[usenames]{xcolor}
\usepackage[giveninits=false,backend=biber,style=nature,style=authoryear,maxcitenames =10, mincitenames=9]{biblatex}
\AtBeginBibliography{\small}
\addbibresource{FJHown23.bib}
\addbibresource{FJH23.bib}
\usepackage{newpxtext}
\usepackage[euler-digits,euler-hat-accent]{eulervm}
\usepackage{media9}
\usepackage[autolinebreaks]{mcode}
\usepackage[tikz]{mdframed}

@@

\renewcommand{\OffTitleLength}{-10ex}
\setlength{\FJHThankYouMessageOffset}{-8ex}
\title{Challenges in Developing Great MCQMC Software}
\author[]{Fred J. Hickernell}
\institute{Department of Applied Mathematics \&
	Center for Interdisciplinary Scientific Computation \\  Illinois Institute of Technology \quad
	\href{mailto:hickernell@iit.edu}{\url{hickernell@iit.edu}} \quad
	\href{http://mypages.iit.edu/~hickernell}{\url{mypages.iit.edu/~hickernell}}}

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and  friends \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Please join us Tuesday, July 19, for lunch at ??? \\ to discuss the future of MCQMC software \\[2ex]
	Thanks to the organizers as we meet again in person\\
	Slides at  \href{??}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022, Linz}
\date[]{July 18, 2022}

@@

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item \textcite{LEc2017a} provides a history of \alert{random number generation}
		\item Notorious \alert{\texttt{randu}} from the 1960s \parencite{RANDU}, which fails the spectral test
		\item \alert{\texttt{VEGAS}} \parencite{Lep78a, Lep21a} importance sampling Monte Carlo algorithm favored by physicists
		\item \alert{ACM} low discrepancy point generators \parencite{BraFox88,BraFoxNie92,HonHic00a}
		\item FinDer \parencite{PasTra95,FinDer} and BRODA \parencite{BRODA20a} targeting quantitative finance
		\item Korobov cubature and scrambled Sobol' generators in \alert{NAG} \parencite{NAG27} for decades		
		\item Scrambled Sobol' and Halton generators in MATLAB \textcite{MAT9.13} since 2008
	\end{itemize}
\end{frame}

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item Keller
		\item L'Ecuyer
		\item Nuyens
		\item Hickernell
		\item TensorFlow
		\item Scrambled Sobol' in SciPy \parencite{virtanen2020scipy} and PyTorch \parencite{paszke2019pytorch}

@@

\begin{frame}{Software Library Architecture}
	content...
\end{frame}

\begin{frame}{Choice of Language}
	content...
\end{frame}

\begin{frame}{Advanced Architectures}
	content...
\end{frame}

\begin{frame}{Introductory Demos}
	content...
\end{frame}

\begin{frame}{Connecting Demos}
	content...
\end{frame}

\begin{frame}{Building User \& Developer Ownership}
	content...
\end{frame}

\begin{frame}{Next Steps}
	content...
\end{frame}

\begin{frame}[allowframebreaks]{References}
	\printbibliography
\end{frame}
